The Iterative Signature Algorithm for Gene Expression data

### 2009-08-10 eisa/inst/doc/EISA_tutorial.Rnw
eisa vignette updates.

The \Rpackage{eisa} includes a simple way to check whether the genes
in a bicluster are associated with a chromosome. See the
\Rfunction{ISA.CHR} function:
<<CHR enrichment>>=
CHR <- ISA.CHR(modules)
summary(CHR,p=0.05)[[11]][,-6]
@

The eleventh bicluster has \Sexpr{summary(CHR,p=0.05)[[11]]$Count[1]} % $
genes on chromosome
\Sexpr{rownames(summary(CHR,p=0.05)[[11]])[1]}. Here is a list of the
genes:
<<CHR enrichment list>>=
unlist(mget(geneIdsByCategory(CHR)[[11]][[1]], org.Hs.egSYMBOL))
@

@@

The enrichment calculation itself is basically the same as for GO and
KEGG, but the \Rfunction{ISA.miRNA} function should be used:
<<miRNA enrichment>>=
if (require(targetscan.Hs.eg.db)) {
  miRNA <- ISA.miRNA(modules)
  summary(miRNA, p=0.05)[[11]]
}
@

@@

The \Rpackage{eisa} package provides some functions to plot parts of
the GO graph that is related to a transcription module. The
\Rfunction{gograph} function creates an object that is a
representation of such a plot. Its input is a table with the GO
categories to plot and their enrichment $p$-values. (Additional
columns are silently ignored.) Here is how to use
it on the previously calculated enrichment scores:
<<goplot1>>=
goplot.2 <- gograph(summary(GO[[1]], p=0.05)[[2]])
@

>>>>

The \Rpackage{eisa} includes a simple way to check whether the genes
in a bicluster are associated with a chromosome. See the
\Rfunction{ISA.CHR} function:
<<CHR enrichment>>=
CHR <- ISA.CHR(modules)
summary(CHR,p=0.05)[[2]][,-6]
@

The second bicluster has \Sexpr{summary(CHR,p=0.05)[[2]]$Count[1]} % $
genes on chromosome
\Sexpr{rownames(summary(CHR,p=0.05)[[2]])[1]}. Here is a list of the
genes:
<<CHR enrichment list>>=
unlist(mget(geneIdsByCategory(CHR)[[2]][[1]], org.Hs.egSYMBOL))
@

@@

The enrichment calculation itself is basically the same as for GO and
KEGG, but the \Rfunction{ISA.miRNA} function should be used:
<<miRNA enrichment>>=
if (require(targetscan.Hs.eg.db)) {
  miRNA <- ISA.miRNA(modules)
  summary(miRNA, p=0.1)[[7]]
}
@

@@

The \Rpackage{eisa} package provides some functions to plot parts of
the GO graph that is related to a transcription module. The
\Rfunction{gograph} function creates an object that is a
representation of such a plot. Its input is a table with the GO
categories to plot and their enrichment $p$-values. (Additional
columns are silently ignored.) Here is how to use
it on the previously calculated enrichment scores:
<<goplot1>>=
goplot.2 <- gograph(summary(GO[[1]], p=0.05)[[1]])
@
